\textbf{Designing a Security Management Layer for CDN Assets}

### 2016-02-15 tex/paper.tex
Added finding for the model

\newpage
\section{Related Terminology}
\subsection{Abbreviations}
\subsubsection{JPF}
Java Path Finder - It was developed by NASA and in 2005 they released it under an open source
licence, which made more people contribute to the project. JPF is usually used for doing model
checking of concurrent programs to easily find for example race conditions and dead locks.

@@

\newpage
\label{sec:model}
\section{Model} \label{sec:model}
The model for this work should show how the data can not be accessed or modified by unauthorized
users and how the defined integrity of the data is always kept in the Perius system.

@@

\subsection{Related work}
The model for this paper is based on the work that was done by Bell, D Elliott, LaPadula and 
Leonard J in their papers \textit{Secure computer systems: Mathematical foundations}~\cite{BLP1} 
and \textit{Secure computer systems: A mathematical model}~\cite{BLP2}. 
In these papers the foundation was laid for how to model a computer system to be able to analyse 
the security of a system. Furthermore this paper was also inspired by Biba, \textit{Integrity 
considerations for secure computer systems}~\cite{BIBA}, where many of the points made by him was 
taken into consideration when inspecting that the integrity of the data was always sound.

@@

The copy-on-write system is only used for files as all of the other objects in the system is
basically just meta data and not classed as important, from an data integrity point of view, as the 
actual files themselves.

@@

In this work external threats are handled as threats that can occur from what has been exposed by
the API (See Section~\ref{sec:API} and internal threats as incorrect implementation. As the server
and its system are assumed safe malicious subsystems are not considered.

@@

@@

\subsection{Interaction of Multiple Accesses} \label{sec:multiple_access}
\fix Rename consequence?
\\
As a result of consequence~\ref{eq:contentupdate} and~\ref{eq:containerupdate} there can be race
conditions where the last write wins. This could be solved by locks or transactions, but as updates
are not based on each other, the trade-off for this inconsistency to scalability and speed is
intentional. However as can also be seen in consequence~\ref{eq:fileupdate}, if a file is
removed from a content that file is not removed from the set of files, even though its modification
process is not the last one to write to the content. This is necessary as a file can be referenced
from several content and the removal process can not atomically ensure that the file is not referred
to by another content. This results in a lot of files in the system which are not referenced from
anywhere. This can be solved by either making each file keep track of how many times it is referred
to and also make it possible to check this number and delete the file in an atomic fashion. An
easier approach would be to have a garbage collector which locks parts of the system momentarily
meanwhile it removes files which are not referenced.
\\
There is also the chance to have content and containers that are not referenced from anywhere and
result in being garbage in the system. This could happen as a result of consequence~\ref{eq:delete}
in combination with any of the other consequences listed in Section~\ref{sec:conseq}. The basic idea
is that an entity is deleted meanwhile another is created or modified to have that entity as its
parent and thus creating a separate tree that can not be reached from the root node of the project.
These type of inconveniences should also be cleaned up by the garbage collector.

@@

@@

As the persistent storage, used in this implementation (Section~\ref{persistent_storage}), does not
implement transactions or locks a lot of different problems can occur when several clients are
working on the same data set at the same time. Such problems could be race conditions and
determining the happened-before relation. In this work this problem is solved by implementing
Copy-on-Write.
\fix Move last paragraph

@@

\subsubsection{Persistent storage}
\label{persistent_storage}
\subsubsubsection{MongoDB}
MongoDB was chosen as the persistent storage because of its quick lookups and because of its
internal storage format called BSON, which is very similar to JSON which the API is using. As the
formats are similar, the process of marshalling and unmarshalling becomes quite easy between the
core code, MongoDB instance and REST interface.  The second reason was that if the system needs to
scale in the future it is very easy to distribute MongoDB and if needed the system can easily be
migrated to Reactive Mongo, which is an asynchronous and non-blocking driver for MongoDB and can
therefore make the system scale even further~\cite{REACTIVEMONGO}.

@@

\subsubsection{Audit logs}

\subsubsection{CDN Connections} \label{sec:cdn_connections}
\fix Describe how the CDN connections are encrypted and secure.

When uploading files to the CDN networks, their TLS/SSL protected APIs are used to ensure that no
data leaks through packet sniffing etc. The files are grouped corresponding to their parent
containers in Perius, which makes it possible to handle the security settings for all files in a
group at once, without having to manually traverse through the tree in Perius.

@@

\newpage
\section{Discussion}
\subsection{Persistent Storage}
More research could have been done in the choosing of persistent storage, as mentioned in ``NoSQL:
Moving from MapReduce Batch Jobs to Event-Driven Data Collection''~\cite{KLINGSBO} many applications
that choose NoSQL databases as their persistent storage actually don't need it. This is most likely
true for Perius too, it would have been efficient enough generating the project trees from an
indexed SQL database with foreign keys. On the other hand it was quite nice having the BSON
documents for insertion as they were so similar the accepted JSON format from the REST service.
As Perius most common operations involve modifying the project tree, a graph database should have 
been researched too.

>>>>

\newpage
\section{Related Terminology}
In this section concepts and abbreviations, that are recurring throughout the paper, which the
reader needs to be familiar with are explained.

\subsection{Abbreviations}
\subsubsection{JPF}
Java Path Finder - It was developed by NASA and in 2005 they released it under an open source
licence, which made more people contribute to the project. JPF is usually used for doing model
checking of concurrent programs to easily find for example race conditions and dead locks.

@@

\subsubsection{Eventual Consistency}
The expression eventual consistency is a term used for describing how data is processed. It is often
used in the context of database systems. Eventual consistency means that stored data is guaranteed 
to be consistent in any one moment, but at some point the data will eventually converge to being 
consistent~\cite{EVENTUAL}.

The effect of this is that persistent storages, especially distributed databases, can
operate faster as there is no need for locks and transactions for any operations. As no locks or
transactions are used, operations on the same entities can be done before earlier operations have
propagated to all nodes. This can mean that the system ends up in a state where there is a conflict
that needs to be handled, for example two operations that wants to change the same data at once. To
solve this the system needs to have defined which operation that will take precedence and this is
usually called conflict or sibling resolution.

\newpage
\section{Model} \label{sec:model}
The model for this work should show how the data can not be accessed or modified by unauthorized
users and how the defined integrity of the data is always kept in the Perius system.

@@

\subsection{Related work}
The model for this paper is based on the work that was done by Bell, D Elliott, LaPadula and 
Leonard J in their papers \textit{Secure computer systems: Mathematical foundations}~\cite{BLP1} 
and \textit{Secure computer systems: A mathematical model}~\cite{BLP2}. 
In these papers the foundation was laid for how to model computer systems to be able to analyse 
the security of them. Furthermore this paper was also inspired by Biba, \textit{Integrity 
considerations for secure computer systems}~\cite{BIBA}, where many of the points made by him was 
taken into consideration when inspecting that the integrity of the data was always sound.

@@

The Copy-on-Write system is only used for files as all of the other objects in the system is
basically just meta data and not classed as important, from an data integrity point of view, as the 
actual files themselves.

@@

In this work external threats are handled as threats that can occur from what has been exposed by
the API (See Section~\ref{sec:API}) and internal threats as incorrect implementation. As the server
and its system are assumed, safe malicious subsystems are not considered.

@@

In this section the consequences of different operations are stated in an informal mathematical
manner. These rules are what should be expected to be followed by the implementation in
Section~\ref{sec:implementation}.

@@

\subsection{Interaction of Multiple Accesses} \label{sec:multiple_access}
\fix Rename consequence?
\\
As a result of consequence~\ref{eq:contentupdate} and~\ref{eq:containerupdate} in
Section~\ref{sec:conseq} there can be race conditions where the last write wins. This could be
solved by locks or transactions, but as updates are not based on each other, the trade-off for this
inconsistency to scalability and speed is intentional. However as can also be seen in
consequence~\ref{eq:fileupdate}, if a file is removed from a content that file is not removed from
the set of files, even though its modification process is not the last one to write to the content.
This is necessary as a file can be referenced from several content and the removal process can not
atomically ensure that the file is not referred to by another content. This results in a lot of
files in the system which are not referenced from anywhere. This can be solved by either making each
file keep track of how many times it is referred to and also make it possible to check this number
and delete the file in an atomic fashion. An easier approach would be to have a garbage collector
which locks parts of the system momentarily meanwhile it removes files which are not referenced.

\par
There is also the chance to have content and containers that are not referenced from anywhere and
result in being garbage in the system. This could happen as a result of consequence~\ref{eq:delete}
in combination with any of the other consequences listed in Section~\ref{sec:conseq}. The basic idea
is that an entity is deleted meanwhile another is created or modified to have that entity as its
parent and thus creating a separate tree that can not be reached from the root node of the project.
These type of inconveniences should also be cleaned up by the garbage collector.

@@

\subsubsection{Conflict Resolution}
If the persistent storage would be distributed the different database nodes would have to have rules
set up for conflict resolution as this model does not consider what to do if the same meta data is
modified on the nodes before they have time to synchronise. The easiest way to handle this is to
have the clocks on the nodes synchronised and timestamp each change and when synchronising the nodes
only consider the newest data if there is a conflict. This will have the same result as concurrent
modification with a single database node with this model, namely last write
wins~\cite{LASTWRITEWINS}.

@@

As the persistent storage, used in this implementation (Section~\ref{sec:persistent_storage}), does not
implement transactions or locks a lot of different problems can occur when several clients are
working on the same data set at the same time. Such problems could be race conditions and
determining the happened-before relation. In this work this problem is solved by implementing
Copy-on-Write.
\fix Move last paragraph

@@

\subsubsection{Persistent storage} \label{sec:persistent_storage}
\subsubsubsection{MongoDB}
MongoDB was chosen as the persistent storage because of its quick lookups and because of its
internal storage format called BSON, which is very similar to JSON which the API is using. As the
formats are similar, the process of marshalling and unmarshalling becomes quite easy between the
core code, MongoDB instance and REST interface.  The second reason was that if the system needs to
scale in the future it is very easy to distribute MongoDB and if needed the system can easily be
migrated to Reactive Mongo, which is an asynchronous and non-blocking driver for MongoDB and can
therefore make the system scale even further~\cite{REACTIVEMONGO}.

@@

\subsubsection{Audit logs}
Audit logs are used in the system to keep track of which users that perform which actions. In the
event that somebody, consciously or unconsciously, are leaking private CDN content from within the
organisation using Perius the audit trail can be used to find which LDAP account that was
responsible for the leak.

\subsubsection{CDN Connections} \label{sec:cdn_connections}
When uploading files to the CDN networks, their TLS/SSL protected APIs are used to ensure that no
data leaks through packet sniffing etc. The files are grouped corresponding to their parent
containers in Perius, which makes it possible to handle the security settings for all files in a
group at once, without having to manually traverse through the tree in Perius.

@@

\newpage
\section{Discussion}
\subsection{Persistent Storage}
More research could have been done in the choosing of persistent storage, as mentioned in 
\textit{``NoSQL: Moving from MapReduce Batch Jobs to Event-Driven Data Collection''}
~\cite{KLINGSBO} many applications that choose NoSQL databases as their persistent storage 
actually don't need it. This is most likely true for Perius too, it would have been efficient 
enough generating the project trees from an indexed SQL database with foreign keys. On the 
other hand it was quite nice having the BSON documents for insertion as they were so similar 
the accepted JSON format from the REST service. As Perius most common operations involve 
modifying the project tree, a graph database should have been researched too.
